\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\author{Thomas Reese and Ben Seefeldt}
\date{November 18, 2013}
\title{Populess: Moving Object Removal from Multiple Static Scene Images}

\begin{document}
\maketitle
\doublespacing

For our project we hope to explore options for the removal of moving objects
from several images of a single scene from a static location. We hope to draw on
numerous techniques learned in the course to develop a method which will be more
robust than a simple median filtering method.

We will develop our method using video input, and hopefully adapt it for use
with images taken in quick succession from a hand-held camera.

We will create an initial composite of the image using na\"ive methods. We will
use these method to create a map of uncertain areas of the image. Treating these
areas as potential holes we will determine the correct pixel from the set of
potential pixels based on object removal techniques. By limiting ourselves to a
set of known, potential pixels we hope to accurately fill ares which contain
complex, or irregular patterns.

We believe using video data will give us the most straightforward way to do
this, as the camera information will remain static. However, provided things in
the first stage of project work proceed easily, it should be straightforward to
modify the image alignment code from the most recent project to allow us to use
fewer images taken from slightly different locations. 

\end{document}
